---
title: "BreedingValue Tables and Figures"
author: "Marc LABADIE"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: 
    toc: yes
    fig_width: 10
    fig_height: 10
    fig_caption: yes
    toc_depth: 5
  html_document: 
    fig_width: 10
    fig_height: 10
    fig_caption: yes
    df_print: kable
    toc: yes
    number_sections: yes
    toc_depth: 5
  pdf_document: 
    toc: yes
    fig_width: 10
    fig_height: 10
    fig_caption: yes
    number_sections: yes
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Graphical parameter}
library(RColorBrewer)
# Graphical parameter
mycolors<- c(brewer.pal(n=11,name = "PRGn"), brewer.pal(n=11,"RdYlBu"))

```

# Import packages and path

```{r import packages and pathdata}
library(ggplot2)
library(RColorBrewer)
library(ggpubr)

#install.packages("https://github/StrawArchitecturalAnalysis")
library(StrawArchitecturalAnalysis)
data_path <- "D:/Mes Donnees/BreedingValue/R/RStrawberryAnalysis/data/raw/"
data_output_path <- "D:/Mes Donnees/BreedingValue/R/RStrawberryAnalysis/data/data_output/"
plot_output_path <- "D:/Mes Donnees/BreedingValue/R/RStrawberryAnalysis/data/plot_output/"

files <- list.files(data_path,full.names = TRUE)
```

# Import data

## Table 1: Plant scale data

```{r import plant scale data }
plant_data <- csv_reader(filepath = files[3],
                         sep = ",",
                         variable.characters = c('Genotype', "modality"),
                         variable.date = c('date'),
                         variable.integer = c("plant",
                                              "no_visible_leaves",
                                              "no_foliar_primodium",
                                              "no_total_leaves",
                                              "no_open_flowers",
                                              "no_aborted_flowers",
                                              "no_closed_flowers",
                                              "no_total_flowers",
                                              "no_fruits",
                                              "no_stolons",
                                              "no_vegetative_bud",
                                              "no_initiated_bud",
                                              "no_floral_bud",
                                              "no_inflorescences",
                                              "no_branch_crown",
                                              "no_extension_crown",
                                              "no_ramifications",
                                              "order_max",
                                              "vid"),
                         date_format = "%d-%m-%Y",
                         timezone = "UTC")

knitr::kable(x = plant_data, 
             align = "c",
             caption = "Table of plant scale data extraction")
```

## Table 2: Module scale data

```{r import module data}
module_data <- csv_reader(filepath = files[1],
                          sep = ",",
                          variable.characters = c("Genotype",
                                                  "modality",
                                                  "type_of_crown",
                                                  "crown_status",
                                                  "stage",
                                                  "complete_module"),
                          variable.date = c('date'),
                          variable.integer = c("plant",
                                               "order",
                                               "no_visible_leaves",
                                               "no_foliar_primordia",
                                               "no_total_leaves",
                                               "no_open_flowers",
                                               "no_aborted_flowers",
                                               "no_total_flowers",
                                               "no_fruits",
                                               "no_stolons",
                                               "no_vegetative_bud",
                                               "no_initiated_bud",
                                               "no_floral_bud",
                                               "vid",
                                               "plant_vid"),
                          date_format = "%d-%m-%Y",
                          timezone = "UTC")


knitr::kable(x = module_data, 
             align = "c",
             caption = "Table of module scale data extraction")
```

## Table 3: node scale data

```{r import node data}
node_data <- csv_reader(filepath = files[2],
                        sep=",",
                        variable.characters = c("branching_type",
                                                "complete",
                                                "Genotype"),
                        variable.integer = c("node_id",
                                             "rank",
                                             "no_modules_branching",
                                             "no_branch_crown_branching",
                                             "no_extension_crown_branching",
                                             "branching_length",
                                             "order",
                                             "plant"),
                        variable.date = c("date"),
                        date_format = "%d-%m-%Y",
                        timezone = "UTC")

knitr::kable(x = module_data, 
             align = "c",
             caption = "Table of node scale data extraction")

```

```{r global parameters}

genotypes<-unique(plant_data[, "Genotype"])

```

# Results

## Plant Scale analysis

### Mean and standard deviation for each variable

#### Table 4: Table of Mean and standard deviation of variable in plant scale data

```{r plant_summarize}
plant_variables <- c("no_visible_leaves",
                     "no_foliar_primodium",
                     "no_total_leaves",
                     "no_open_flowers",
                     "no_aborted_flowers",
                     "no_closed_flowers",
                     "no_total_flowers",
                     "no_fruits",
                     "no_stolons",
                     "no_vegetative_bud",
                     "no_initiated_bud",
                     "no_floral_bud",
                     "no_inflorescences",
                     "no_branch_crown",
                     "no_extension_crown",
                     "no_ramifications",
                     "order_max")

plant_summarize <- summarize_extract_plant(plant_data,variables = plant_variables)

knitr::kable(x = plant_summarize, 
             align = "c",
             caption = "Table of Mean and standard deviation of variable in plant scale data",
             digits = 2)

write.csv(plant_summarize,paste(data_output_path,"plant_summarize.csv"), row.names = FALSE)
```

#### Figure 1: Pointwise mean for each variable according date at plant scale

```{r Figure 1, fig.cap="Figure 1: PointWise mean at plant scale", fig.height=8, fig.width=8}

plot_variables <- c("no_total_leaves","no_stolons","no_total_flowers","no_fruits") 
plots <- list()


for(plot_variable in plot_variables){
  message(plot_variable)
  
  plots[[plot_variable]]<- local({
    plot_pointwisemean(data = plant_summarize, scale = "plant", variable = plot_variable,display_sd = FALSE)+
      scale_colour_manual(values = mycolors)
  })
}


figure_1<- ggarrange(plots$no_total_leaves + theme(legend.position="none") + labs(title = NULL),
                   plots$no_stolons + theme(legend.position="none") + labs(title = NULL),
                   plots$no_total_flowers + theme(legend.position="none") + labs(title = NULL),
                   plots$no_fruits + theme(legend.position="none") + labs(title = NULL),
                   common.legend = TRUE, 
                   legend="bottom",
                   labels = c("A","B","C","D"),
                   ncol = 2, nrow = 2)

annotate_figure(p = figure_1,
                top = text_grob(label = " ",just = "centre", size = 25),
                fig.lab = "Figure 1: Pointwise mean number", fig.lab.face = "bold",fig.lab.size = 14)

ggsave(paste(plot_output_path,"Fig1.png"), units="in", width=8, height=8, dpi=800)

```

### Stage distributions

#### Table 5: Table of stage distribution at plant scale

```{r stage distribution at plant scale}
dist <- distribution.stage(data = module_data)

knitr::kable(x = dist,
             digits = 2,
             caption = "Table of stage distribution at plant scale")

write.csv(plant_summarize,paste(data_output_path,"stage_distribution_plant_scale.csv"), row.names = FALSE)

```

#### Figure 2: Pie chart of stage repartition for all genotypes

```{r Pie Chart representation, fig.cap="Figure 2: Pie chart representation at Plant scale",fig.height=10,fig.width=10  }

pieplots <- list()

for (genotype in genotypes){
  date <-unique(dist[dist[, "Genotype"]==genotype,"date"])
  pieplots[[genotype]] <- local({
    plot_pie.stage(data = dist, genotype = genotype, date = date)+
      scale_fill_manual(values = mycolors)
  })
}

figure_2<- ggarrange(pieplots$Belle_et_Bonne + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Belrubi + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$CF10122 + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$CF10277 + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$CF12074 + 
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$CF9416 + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Ciflorette + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Cigaline + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$CIR107 + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Cireine + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Clery + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Darselect +
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$Dream + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$gariguette + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$`Leroy Ladurie` +
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$Magnum +
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Manon + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     pieplots$Moutot +
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$Osiris + 
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$Rubis +
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$Sanié +
                       theme(legend.position="none") +
                       labs(title = NULL),
                     pieplots$`Sans rivale` +
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     legend = "right",
                     common.legend = TRUE,
                    labels = "AUTO",
                    ncol = 5, nrow = 5)

annotate_figure(p = figure_2,
                top = text_grob(label = " "),
                fig.lab = "Figure 2: Pie chart of stage repartition for all genotypes", 
                fig.lab.face = "bold",
                fig.lab.size = 14)

ggsave(paste(plot_output_path,"Fig2.png"), units="in", width=10, height=10, 
       dpi=800)

```

## Module scale anlysis

### Mean and standard deviation at module scale

#### Table 6: Table of Mean and standard deviation of variable in module scale data

```{r summarize module data}
module_variables <- c("no_visible_leaves",
                      "no_foliar_primordia",
                      "no_total_leaves",
                      "no_open_flowers",
                      "no_aborted_flowers",
                      "no_total_flowers",
                      "no_fruits",
                      "no_stolons",
                      "no_vegetative_bud",
                      "no_initiated_bud",
                      "no_floral_bud")

module_summarize <- summarize_extract_module(module_data, variables = module_variables)

knitr::kable(x = module_summarize, 
             align = "c",
             caption = "Table of Mean and standard deviation of variable in plant scale data",
             digits = 2)

write.csv(plant_summarize,paste(data_output_path,"module_summarize.csv"), row.names = FALSE)
```

#### Figure 3: Pointwise mean according to module order for all genotypes

```{r pointwise mean for each variable by genotype and order}

plot_variables <- c("no_total_leaves","no_stolons","no_total_flowers","no_fruits") 

 

plot_lists <-list()

for(plot_variable in plot_variables){
    message(plot_variable)
    plot_lists[[plot_variable]] <- local({
      plot_pointwisemean(data = module_summarize, scale = "module", variable = plot_variable,display_sd = FALSE)+
        scale_colour_manual(values = mycolors)
    })
  }


figure_3<- ggarrange(plot_lists$no_total_leaves+ 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     plot_lists$no_stolons + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     plot_lists$no_total_flowers + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                     plot_lists$no_fruits + 
                       theme(legend.position="none") + 
                       labs(title = NULL),
                   common.legend = TRUE, 
                   legend="right",
                   labels = c("A","B","C","D"),
                   ncol = 2, nrow = 2)

annotate_figure(p = figure_3,
                top = text_grob(label = " ",just = "centre", size = 25),
                fig.lab = "Figure 3: Pointwise mean according to module order for all genotypes", 
                fig.lab.face = "bold",
                fig.lab.size = 12)

ggsave(paste(plot_output_path,"Fig3.png"), units="in", width=8, height=8, dpi=800)


```

#### Statistical test: Comparison between genotype and order

```{r kruska wallis test}
k_test_table<- list()

for (module_variable in module_variables){
  
  k_test_table[[module_variable]]<- local({
    test.kruskal(data = module_data, 
                 variable = "no_total_leaves", 
                 letter = TRUE, 
                 trt = interaction(module_data[, "Genotype"], 
                                   module_data[, "order"]),
                 display = FALSE, 
                 )
    
    }
    )
}

kruskal_ouput<-list()
for (module_variable in module_variables){
  kruskal_ouput[[module_variable]]<-local({
    merge(k_test_table[[module_variable]]$means,
          k_test_table[[module_variable]]$groups,
          by='row.names')
  }) 
}

```

##### Table 7: ANOVA on the rank (kuskal wallis) for no. total leaves

```{r output kruskal no total of leaves}

knitr::kable(x = kruskal_ouput$no_total_leaves[,-c(11)],
             digits = 2,
             caption = "ANOVA on the rank (kuskal wallis) for no. total leaves")

write.csv(kruskal_ouput$no_total_leaves[,-c(11)],
          paste(data_output_path,"kruskal_no.leaves.csv"), row.names = FALSE)
```

##### Table 8: ANOVA on the rank (kuskal wallis) for no. total flowers

```{r output test kruskal no total of total flowers}
knitr::kable(x = kruskal_ouput$no_total_flowers[,-c(11)],
             digits = 2,
             caption = "ANOVA on the rank (kuskal wallis) for no. total flowers")

write.csv(kruskal_ouput$no_total_flowers[,-c(11)],
          paste(data_output_path,"kruskal_no.total_flowers.csv"), row.names = FALSE)
```

##### Table 9: ANOVA on the rank (kuskal wallis) for no. total flowers

```{r output test kruskal no stolons}
knitr::kable(x = kruskal_ouput$no_stolons[,-c(11)],
             digits = 2,
             caption = "ANOVA on the rank (kuskal wallis) for no. stolons")

write.csv(kruskal_ouput$no_stolons[,-c(11)],
          paste(data_output_path,"kruskal_no.stolons.csv"), row.names = FALSE)
```

##### Table 10: ANOVA on the rank (kuskal wallis) for no. total flowers

```{r output test kruskal no total of fruits}
knitr::kable(x = kruskal_ouput$no_fruits[,-c(11)],
             digits = 2,
             caption = "ANOVA on the rank (kuskal wallis) for no. fruits")

write.csv(kruskal_ouput$no_fruits[,-c(11)],
          paste(data_output_path,"kruskal_no.fruits.csv"), row.names = FALSE)
```

### crown type distribution

#### Table 11: Crown type distribution data

```{r crown type distribution data}
crown_type_distribution <- distribution.crown_type(data = module_data)
knitr::kable(x = crown_type_distribution,
             digits = 2,
             caption = "Crown_type distribution",
             align = "c")

write.csv(crown_type_distribution,
          paste(data_output_path,"crown_type_distribution.csv"), row.names = FALSE)
```

#### Figure 4: Frequency distribution of branch crown

```{r frequency distribution of branch crown, fig.cap="frequency distribution of branch crown", fig.height=8, fig.width=8}

figure_4 <- plot_distribution.crown_type(data = crown_type_distribution,
                                         crown_type = "Branch",
                                         variable = "freq") +
                labs(title = " ") + 
                scale_colour_manual(values = mycolors)

annotate_figure(p = figure_4,
                top = text_grob(label = " ",just = "centre", size = 25),
                fig.lab = "Figure 4:Frequency distribution of branch crown for all genotypes", 
                fig.lab.face = "bold",
                fig.lab.size = 12)

ggsave(paste(plot_output_path,"Fig4.png"), units="in", width=8, height=8, dpi=800)


```

#### Figure 5: Relative frequency of branch crown

```{r Relative frequency distribution of branch crown,fig.cap="Relative frequency distribution of branch crown", fig.height=8, fig.width=8}

figure_5 <- plot_distribution.crown_type(data = crown_type_distribution,
                                         crown_type = "Branch",
                                         variable = "prob") +
                labs(title = " ") + 
                scale_colour_manual(values = mycolors)

annotate_figure(p = figure_4,
                top = text_grob(label = " ",just = "centre", size = 25),
                fig.lab = "Figure 5:Relative frequency distribution of branch crown for all genotypes", 
                fig.lab.face = "bold",
                fig.lab.size = 12)

ggsave(paste(plot_output_path,"Fig5.png"), units="in", width=8, height=8, dpi=800)


```

## Node scale analysis

### Mean and standard deviation at node scale

```{r node summarize}
variables <- c("no_modules_branching",
               "no_branch_crown_branching",
               "no_extension_crown_branching",
               "branching_length")

node_summarize <- summarize_extract_node(data = node_data, variables = variables)

knitr::kable(x = node_summarize,
             digits = 3,
             caption = "Table of Mean and standard deviation of variable at node scale",
             align = "c")


write.csv(node_summarize,
          paste(data_output_path,"node_summarize.csv"), row.names = FALSE)
```

### Axillary production distribution

#### Table 12: Table of axillary production distribution

```{r Table of axillary production distribution}
axillary_production <- distribution.axillary_production(node_data)
knitr::kable(x = axillary_production,
             digits = 2,
             align = "c",
             caption = "Table of axillary production distribution")

write.csv(axillary_production,
          paste(data_output_path,"axillary_production.csv"), row.names = FALSE)
```

#### Figure 6 : Axillary production plot according to rank node frequency

```{r plot axillary production distribution, fig.height=10, fig.width=10}

plots_axillary_production<- list()
for (genotype in genotypes){
  plots_axillary_production[[genotype]] <- local({
    plot_axillary_production(data = axillary_production,
                         genotype = genotype,
                         variable = "n")
  })
}

figure_6<- ggarrange(plots_axillary_production$Belle_et_Bonne + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Belrubi +
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF10122 +
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF10277 + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF12074 +
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF9416 + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Ciflorette + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Cigaline + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CIR107 + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Cireine + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Clery + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Darselect + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Dream + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$gariguette + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$`Leroy Ladurie` + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Magnum + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Manon + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Moutot + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Osiris + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Rubis +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Sanié + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$`Sans rivale` + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     legend = "right",
                     common.legend = TRUE,
                     labels = "AUTO",
                      ncol = 5, nrow = 5)

annotate_figure(p = figure_6,
                top = text_grob(label = " "),
                fig.lab = "Figure 6: Axillary production repartition for all genotypes at order0", 
                fig.lab.face = "bold",
                fig.lab.size = 14)

ggsave(paste(plot_output_path,"Fig6.png"), units="in", width=10, height=10, dpi=800)

```

#### Figure 7: Relative frequency axillary production

```{r plot prob axillary production distribution, fig.height=10, fig.width=10}
plots_axillary_production<- list()
for (genotype in genotypes){
  plots_axillary_production[[genotype]] <- local({
    plot_axillary_production(data = axillary_production,
                         genotype = genotype,
                         variable = "prob")
  })
}

figure_7<- ggarrange(plots_axillary_production$Belle_et_Bonne +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Belrubi +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF10122 +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF10277 +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF12074 +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CF9416 +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Ciflorette +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Cigaline +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$CIR107 +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Cireine +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Clery +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Darselect +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Dream +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$gariguette +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$`Leroy Ladurie` +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Magnum +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Manon +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Moutot +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Osiris +
                       theme(legend.position="none") +
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Rubis +
                       theme(legend.position="none") +
                      labs(title = NULL)+
                      scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$Sanié +
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     plots_axillary_production$`Sans rivale` + 
                       theme(legend.position="none") + 
                       labs(title = NULL)+
                       scale_colour_brewer(type = "qual",palette = 6),
                     legend = "bottom",
                     common.legend = TRUE,
                     labels = "AUTO",
                      ncol = 5, nrow = 5)

annotate_figure(p = figure_7,
                top = text_grob(label = " "),
                fig.lab = "Figure 7: Axillary production repartition for all genotypes at order0", 
                fig.lab.face = "bold",
                fig.lab.size = 14)

ggsave(paste(plot_output_path,"Fig7.png"), units="in", width=10, height=10, dpi=800)

```
